The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2021-08-27 src/paper/results/scenarios.tex
Various fixes that got lost in the previous PR.

\subsection{Scenarios} \comment[id=K]{Add parameter notation when writing this.}
\label{subsec:appendix_scenarios}

@@

>>>>

\subsection{Scenarios}
\label{subsec:appendix_scenarios}

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December onward. Some states started opening
them gradually in late February, but operation at normal capacity did not resume until
the beginning of June. Figure~\ref{fig:school_scenarios} shows the effects of different
policies regarding schools starting after Easter, at which point rapid tests had become
widely available. We estimate the realized scenario to have essentially the same effect
as a situation with closed schools. Under fully opened schools with mandatory tests,
total infections would have been 6\% higher; this number rises to 20\% without tests.
These effect sizes are broadly in line with empirical studies (e.g. \citet{Vlachos2021,
Berger2021}, see Section~\ref{subsec:model_validation} for a comparison). In light of the
large negative effects school closures have on children and parents \citep{Luijten2021,
Melegari2021}---and in particular on those with low socio-economic status---these results
in conjunction with hindsight bias suggest that opening schools combined with a testing
strategy would have been beneficial. In other situations, and particular when rapid test
are not available at scale, trade-offs may well be different.

\begin{figure}[!tp]
    \centering

    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{Effects of different schooling scenarios}}
        \label{fig:school_scenarios}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/new_work_scenarios/full_newly_infected}
        \caption{{Effects of different work scenarios}}
        \label{fig:workplace_scenarios}
    \end{subfigure}
    \vskip3ex

    \caption{Effects of different scenarios for policies regarding schools and workplaces.}
    \label{fig:school_workplace_scenarios}

    \floatfoot{\noindent \textit{Note:} Blue lines in both figures refer to our baseline
        scenario; they are the same as in
        Figure~\ref{fig:2021_scenarios_newly_infected}. Interventions start at Easter
        because there were no capacity constraints for rapid tests afterwards.
        For legibility reasons, all lines are rolling 7-day averages.}

\end{figure}

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of workers
receiving tests, testing at the workplace has larger effects than mandating employees to
work from home. Whether the share of workers working at the usual workplace is reduced
or increased by ten percent changes infection rates by 2.5\% or less in either
direction. Making testing mandatory twice a week---assuming independent compliance by
employers and workers of 95\% each---would have reduced infections by 23\%. Reducing
rapid tests offers by employers to the level of March would have increased infections by
13\%.
